---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# RMarkdown Reproducibility Example

<!-- badges: start -->

<!-- badges: end -->

This is a template RMarkdown document which follows minimal reproducibility best practices.

## Dependencies

In this section, you should describe dependencies needed to execute your code. 

### System Dependencies

Make sure to list all system dependencies needed to execute your code. For example, if you use R's built-in pipe operator `|>`, then your code depends on R version at least 4.1. If you use R's stan package, then you need V8 as a system dependency.

At the very least, you should provide a list of dependencies such as:
```yaml
dependencies:
  - R>=4.1  # https://www.r-project.org/
  - V8  # https://v8.dev/
```

### R Package Dependencies

R packages dependencies can be managed and installed directly in your code. For this, I recommend using the **pacman** package:

```{r pacman}
if (!require(pacman)) install.packages("pacman")

pacman::p_load(ggplot2)  # This installs and loads `ggplot`
```


## Code and Analyses

In this section, you should place all of your code and analyses.

### Managing Figures

If you generate figures for an external document, then make sure to both display the figures and save them automatically to a subfolder. Note that the subfolder may not exist on the computer of the person running your code. As such, you should create if if it does not already exist:

```{r figure}
fig <- ggplot(pressure) +
  geom_point(aes(x=temperature, y=pressure))

dir.create("output", showWarnings=FALSE)
ggsave("output/pressure_plot.pdf", fig)

show(fig)
```

## System Information

In this section, provide information about the system that was used to execute the RMarkdown document. This information can be generated automatically as follows:

```{r}
sessionInfo()
```

